Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model

### 2012-02-05 Multiresolution_framework/ltx/manuscript.tex
minor change
added a paper from Breakspear
general correction

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{setspace}                               
\usepackage[usenames,dvipsnames]{color}  
%This bit is how to use hyperlink without stupid coloured rectangles around it
\usepackage{float}
\usepackage{hyperref}
\hypersetup{colorlinks,linkcolor=black,filecolor=black,urlcolor=black,citecolor=black}

@@

\section{IDE Neural Field Model}
\singlespacing
\begin{table*}[!t]
\begin{tabular}{|l|l|l|}
	\hline
	\textbf{Symbol} & \textbf{Quantity} & \textbf{Units}\\
	\hline
	\multicolumn{3}{|c|}{\emph{Domain and indices}}\\
	\hline
	$\Omega$ & Spatial domain & n.a.\\
	$\mathbf{r}$ & Spatial location & [mm, mm]\\
	$t$ & Time & s\\
	\hline
	\multicolumn{3}{|c|}{\emph{Model}}\\
	\hline
    $y_t$ & Observation & mV\\
    $v(\mathbf{r},t)$ & Mean membrane potential & mV \\
	$f(v\left(\mathbf{r},t\right))$ & Firing rate function & spikes.s$^{-1}$\\
	$e_t(\mathbf{r})$ & Field disturbance, with covariance function $\eta(\mathbf r-\mathbf r')$ & mV\\
	$\boldsymbol\varepsilon_t$ & Observation noise, with covariance matrix $\Sigma_\varepsilon$ & mV\\
	$m(\mathbf{r}_n)$ & Observation kernel where $n$ is sensor index $n=1,..,n_y$ & n.a. \\
	$w(\mathbf{r})$ & Spatial connectivity kernel & n.a.\\
	$h(t)$ & Post-synaptic response kernel & mV\\
	$\tau$, $\xi$ & Membrane time constant \& time constant parameter & s, n.a.\\
	$\delta(t)$ & Dirac-delta function & n.a.\\
	\hline    
	\multicolumn{3}{|c|}{\emph{Multi-resolution Approximation}} \\
	\hline                                                   
	$\phi_{j,l}(r)$&Scaling function&n.a\\
	$\psi_{j,l}(r)$&Wavelet function&n.a\\  
	$\alpha_{j_0,l}, \beta_{j,l}$&Connectivity kernel approximation and detail coefficients&mV~spike$^{-1}$\\ 
	$x_{t,j_{0},l},\check{x}_{t,j,l}$&Field approximation and detail coefficients at a given time&mV~spike$^{-1}$\\ 
	$N_m(r)$&$m$-th order B-spline function&n.a.\\
	$\varphi_m(r)$&$m$-th order B-spline wavelet function&n.a.\\
	\hline
	\multicolumn{3}{|c|}{\emph{Reduced Model}} \\
	\hline
		$\boldsymbol\mu(r)$&Vector of $n_x$ field scaling and wavelet functions&n.a.\\
		$\boldsymbol\lambda(r)$&Vector of $n_{\boldsymbol\theta}$ connectivity kernel scaling and wavelet functions&n.a.\\
   	$\mathbf{x}_t$ & State vector at time $t$ composed of  $x_{t,j_{0},l}$ and $\check{x}_{t,j,l}$ & mV\\ 
		$\boldsymbol\theta$&Vector of connectivity kernel parameters composed of $\alpha_{j_0,l}$ and $\beta_{j,l}$&mV\\ 
		$\boldsymbol{\Lambda}_x$&Inner product of field basis functions&n.a.\\
		$\boldsymbol\Gamma, \boldsymbol\Lambda_{\boldsymbol{\theta}}$&Decomposition connectivity matrices&n.a.\\
   	$\mathbf{w}_t$ & State disturbance vector, with covariance $\Sigma_w$ & mV\\ 
    $\mathbf{A}(\boldsymbol{\theta})$& State transition matrix& n.a.\\
   	$\mathbf{C}$ & Observation matrix & n.a. \\
	\hline
	\multicolumn{3}{|c|}{\emph{Frequency Analysis}} \\
	\hline
	$\boldsymbol{\nu}$, $\boldsymbol{\nu}_c$ & spatial frequency and spatial cutoff frequency & cycles/mm \\
	$\sigma_{\nu}^2$ & variance of Fourier transformed Gaussian basis function & (cycles/mm)$^2$\\
	\hline
	\multicolumn{3}{|c|}{\emph{Estimation}} \\
	\hline
	$\hat{\mathbf{x}}_t^{f-}$, $\hat{\mathbf{x}}_t^f$ & Forward prior and posterior state estimates & mV\\
	$\hat{\mathbf{x}}_t^{b}$ & Backward posterior state estimates & mV\\
	$P^{f-}_t$, $P^f_t$  & Forward prior and posterior covariance matrices & mV$^2$\\
	$P^b_t$ & Backward posterior covariance matrices & mV$^2$\\
	$M_t$& Cross-covariance matrix & mV$^2$\\
	$\mathcal K_{t} $ & Filter gain & n.a.\\ 
	$\mathcal S_{t} $ & Smoother gain & n.a.\\ 
	$\boldsymbol\Xi_1, \boldsymbol\Xi_0$&Expected covariance and cross-covariance matrices& mV$^2$\\ 
	$\mathcal{Q}(\boldsymbol{\theta},\boldsymbol\theta')$&Lower bound on log-likelihood function&n.a.\\
	$\boldsymbol\nu_0$, $\boldsymbol\nu_1$, $\boldsymbol\Upsilon$&Lower bound coefficient matrices&??\\
	\hline
\end{tabular}
\caption{\textbf{Notation.} The first column of the table gives the symbols for all the notation used in the paper. The second column provides a brief description of the quantity, and the third column provides the SI units where relevant.}
\label{tab:Notation}
\end{table*}  
\doublespacing

The single layer homogeneous neural field model in the most general form is described by the equation
\begin{equation}
	\label{FullDoubleIntModel} \underbrace{v\left(\mathbf{r},t\right)}_{\text{field}} =
	\int_{-\infty}^t 
	\underbrace{h\left(t - t'\right)}_{\text{synapse}} \int_\Omega
	\parham{\theta}\underbrace{w\left(\mathbf{r},\mathbf{r}'\right)}_{\text{connectivity}} 
	\underbrace{f\left( v\left( \mathbf{r}',t' \right)\right)}_{\text{firing}}
	\, \mathrm{d}\mathbf{r}'\mathrm{d}t',
\end{equation}
where the post-synaptic membrane voltage at time $t$ of a population of neurons at position $\mathbf r$ within the spatial domain $\Omega$ is denoted by $v\left(\mathbf r,t\right)$. The function $h(t)$ describes the post-synaptic response kernel, $w(\mathbf{r})$ describes the connectivity kernel and $f(v(\mathbf{r},t))$ describes the relationship between the mean membrane potential and the mean firing rate. The parameter $\theta$ can be thought of the synaptic efficiency or coupling strength, where $\theta>0$ and $\theta<0$ describes excitation and inhibition, respectively. There are various forms of $h(t)$ that have been proposed in the literature, with different levels of complexity. These are shown in Fig.~\ref{fig:Modelcomponents}. Similarly, both the connectivity kernel and the activity function (firing rate) can take various forms. These are also shown in Fig.~\ref{fig:Modelcomponents}. The form of $w(\mathbf{r})$ typically describes an Laplacian (exponential) or Gaussian decay in connectivity strength from any point in the field. By assuming the form of $h(t)$ is the same across layers (scales) the Amari style neural field model is formed, incorporating a multilayer structure into the connectivity kernel. In this way, the connectivity kernel typically takes the form of a Mexican hat (Gaussian shape within layer connectivity) or Wizard hat (Laplacian shape within layer) as depicted in Fig.~\ref{fig:Modelcomponents}.

@@

The observation equation describing the intracranial electrophysiological recordings is given by
\begin{equation}\label{eq:ObservationEquation}
	y_t(\mathbf{r}_{n_y}) = \int_{\Omega} { m\left(\mathbf{r}_{n_y}-\mathbf{r}'\right) v_t\left(\mathbf{r}'\right) \, \mathrm{d}\mathbf{r}'} + \boldsymbol\epsilon_t(\mathbf{r}_{n_y}), 
\end{equation}
where $m\left(\mathbf{r}_{n_y}-\mathbf{r}'\right)$ is the observation kernel at location $\mathbf{r}_{n_y}$ and  $\boldsymbol{\epsilon}_{t}\sim \mathcal{N}\left(\mathbf{0},\mathbf{\Sigma}_{\epsilon}\right)$  is an i.i.d. Gaussian white noise process and the covariance matrix $\mathbf{\Sigma}_{\epsilon}=\sigma^2_{\epsilon}\mathbf I_{n_y}$, where $\mathbf I$ denotes the identity matrix. \parham{The lead field parameters are not included in the observation equation as the intracranial recordings are considered here.}

@@

% At each spatial scale indexed by $j$ (level of decomposition), the neural field can be written as
% \begin{equation}
% 	v_{j,t}\left(\mathbf{r}\right) = \begin{cases}
% 	\sum_{l \in \mathbb{Z}}x_{j,l}(t) \underbrace{\phi_{j,l}\left(\mathbf{r}\right)}_{\text{scaling function}} + \check{x}_{t,j,l}\underbrace{\psi_{j,l}\left(\mathbf{r}\right)}_{\text{mother wavelet}} & \text{if $j=0$},\\
% 	\sum_{l \in \mathbb{Z}}\check{x}_{t,j,l}\psi_{j,l}\left(\mathbf{r}\right) & \text{otherwise}
% \end{cases}
% \end{equation}
The dynamic neural field is decomposed using
\begin{equation}
 v_t\left(r\right)=\sum_{l \in \mathbb{Z}}x_{t,j_{0},l} \underbrace{\phi_{j_0,l}\left(r\right)}_{\text{scaling functions}} + \sum_{j\geq j_0}^{\infty} \sum_{l \in \mathbb{Z}^n} \check{x}_{t,j,l} \underbrace{\psi_{j,l}\left(r\right)}_{\text{wavelets}},
\label{eq:FieldExpansion}
\end{equation}
where $x_{t,j_{0},l}$ and $\check{x}_{t,j,l} $ are the dynamic coefficients of the expansion, constituting the state vector at time $t$. The decomposition enables a separation of the static spatial characteristics, which are considered static functions, that are weighted by dynamic coefficients.

@@

\boldsymbol\theta^\top \triangleq& [\begin{array}{ccccc} \boldsymbol\alpha_{j_0}^\top & \boldsymbol\beta_{j_0}^\top & \boldsymbol\beta_{j_0+1}^\top & \cdots & \boldsymbol\beta_{J}^\top \end{array}] 

@@

\mathbf{x}_{t}^\top \triangleq& [\begin{array}{ccccc}\mathbf{x}_{t,j_{0}}^\top &  \check{\mathbf{x}}_{t,j_{0}}^\top & \check{\mathbf{x}}_{t,j_{0}+1}^\top & \cdots & \check{\mathbf{x}}_{t,J}^\top\end{array}]

@@

\boldsymbol\psi_{J}^\top(r)\end{array}\right] \\

@@

\boldsymbol\psi_{J}^\top(r)\end{array}\right],

@@

\parham{The state-transition equation can be simplified if the chosen family of wavelets are isotropic where}

@@

	\boldsymbol{\lambda}_{j,l}(r-r') = \boldsymbol{\lambda}(2\mathbf{c}_{j,l}+r'-r). 

@@

Following this, we can switch the order of operations with the inner product and convolution in Eq.~\eqref{eq:ApproxDiscreteTimeModel4}. With this switch the convolution is now between the scaling functions and wavelets for the field and the scaling functions and wavelets for the connectivity kernel. This convolution can be calculated analytically when using B-spline wavelets and can be predefined once, since these are static functions. This has major computation advantages when solving the estimation problem. \parham{Although this switch holds theoretically it should be noted that it will introduce numerical error, specially close to the edges, due to the finite extent of the field. } The predefined convolution can be written as

@@

	\left[\Gamma(r')\right]_{:j,l} = T_s \mathbf{\Lambda}_{x}^{-1}\int_{\Omega} \boldsymbol\mu\left(r\right)\boldsymbol\lambda\left(2c_{j,l} + r'-r\right) \,\mathrm{d}r,

@@

giving

@@

	\mathbf{y}_t = \mathbf{C}\mathbf{x}_t + \boldsymbol{\varepsilon}_t,

@@

In this paper, we have presented a novel model-based framework for estimating cortical dynamics from electrophysiological measurements. The novel and key developments of the paper include the multi-resolution FEM representation of the neural field, and the estimator for an intracortical connectivity kernel with an arbitrary shape. This work is significant, as the ability to create patient specific neural field models has the potential to contribute to our understanding and improve treatment of diseases resulting from abnormal neurodynamics, such as epilepsy. Other groups have previously highlighted the importance of a multi-resolution approach in neural field modeling. It is thought that the dynamics and connectivity structure differs at different spatial scales~\citep{Qubbaj2009,Breakspear2005}. %\dean{This is a test to see if we can fit something about Breaky's paper in here. It would be nice to slot something in here because he used wavelets.}

@@

Another extension of this framework is the inclusion of finite distant-dependent action potential propagation velocity into the parametric neural field equations. In small networks the delays via propagation can be neglected, however they must be accounted for in large scale networks. For instance, it is shown by \citet{Ghosh2008} that inclusion of time delays arising from propagation along connecting \parham{fibres} are essential for the fluctuations to be appeared in the default networks. Finally, future work should be directed towards applying and validating the framework on real data.

\appendix
\section{Inner product of two B-spline scaling functions}\label{ap:InnerProductOfBsplines}
In this section, an analytic formula is derived for the inner product of two B-spline scaling functions. Consider two B-spline scaling functions of order $m$ and $m'$. The support of $N_m\left(s\right)$ is $\left[ 0,m\right]$ and  is symmetric with respect to $r=\frac{m}{2}$, i.e.
\begin{align}\label{eq:APP-SymmetrySplieEq}
 N_{m}\left(\frac{m}{2}+r\right)=N_{m}\left(\frac{m}{2}-r\right).
\end{align}
A direct consequence of Eq.~\eqref{eq:APP-SymmetrySplieEq} is 
\begin{align}
 N_{m}\left(r\right)=N_{m}\left(m-r\right).
\end{align}
Therefore
\begin{align}
\int_{-\infty}^{+\infty}N_{m}\left(r-l_{1}\right)N_{m'}\left(r-l_{2}\right)dr&=\int_{-\infty}^{+\infty}N_{m}\left(m-r+l_{1}\right)N_{m'}\left(r-l_{2}\right)dr \nonumber \\
&=\int_{-\infty}^{+\infty}N_{m}\left(m+l_{1}-l_{2}-u\right)N_{m'}\left(u\right)du \nonumber \\
&=\left(N_m \ast N_{m'}\right) \left(m+l_{1}-l_{2}\right) \nonumber \\
&=N_{m+m'}\left(m+l_{1}-l_{2}\right) \nonumber \\
&=N_{m+m'}\left(m'+l_{2}-l_{1}\right).
\end{align}
\section{Scaling function expansion}\label{ap:Induction}  
In this appendix we show by induction that how the scaling function at $j=0$ can be written in terms of the scaling function at level $j$. For $n_1$ in  Eq.~\eqref{eq:MRA-ConvertingFormulaForscalingFunctions} we have
\begin{align}
 N_{m}\left(r\right)&=\sum_{n_1=0}^{m} \left[\mathbf p\right]_{n_1} N_{m}\left(2r-n_1\right) \label{eq:App-TwoScalepair1},
  \end{align}
which clearly holds from two-scale relation pair (see Eq.~\eqref{eq:MRA-TwoScalepair1}). Now assuming Eq.~\eqref{eq:MRA-ConvertingFormulaForscalingFunctions} for $n_{j-1}$ we can write 
\begin{align}\label{eq:app-ConvertingFormulaForscalingFunctions}
 &N_m(r)=\nonumber \\
&\sum_{n_1,n_2, \dots n_{j-1}=0}^{m}\left[\mathbf p\right]_{n_1} \left[\mathbf p\right]_{n_2}\dots \left[\mathbf p\right]_{n_{j-1}}N_m(2^{j-1}r-k_{n_1,n_2, \dots, n_{j-1}}),
\end{align}
in which $N_m(2^{j-1}r-k_{n_1,n_2, \dots, n_{j-1}})$ can be written in terms of $N_m(2^{j}r)$ as
\begin{align}\label{eq:AppendixNj-1intermsofNj}
 &N_m(2^{j-1}r-k_{n_1,n_2, \dots, n_{j-1}})=\nonumber \\
&\sum_{n_j=0}^m \left[\mathbf p\right]_{n_j}N_m(2^jr-2\times k_{n_1,n_2, \dots, n_{j-1}}-n_j)\nonumber \\
&=\sum_{n_j=0}^m \left[\mathbf p\right]_{n_j}N_m(2^jr- k_{n_1,n_2, \dots, n_{j}}).
\end{align}
Substituting Eq.~\eqref{eq:AppendixNj-1intermsofNj} into Eq.~\eqref{eq:MRA-ConvertingFormulaForscalingFunctions} completes the proof.

>>>>

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{setspace}                               
\usepackage[usenames,dvipsnames]{color}  
%This bit is how to use hyperlink without  coloured rectangles around it
\usepackage{float}
\usepackage{hyperref}
\hypersetup{colorlinks,linkcolor=black,filecolor=black,urlcolor=black,citecolor=black}

@@

\section{IDE Neural Field Model}
\singlespacing
\begin{table*}[!t]
\begin{tabular}{|l|l|l|}
	\hline
	\textbf{Symbol} & \textbf{Quantity} & \textbf{Units}\\
	\hline
	\multicolumn{3}{|c|}{\emph{Domain and indices}}\\
	\hline
	$\Omega$ & Spatial domain & n.a.\\
	$\mathbf{r}$ & Spatial location & [mm, mm]\\
	$t$ & Time & s\\
	\hline
	\multicolumn{3}{|c|}{\emph{Model}}\\
	\hline
    $y_t$ & Observation & mV\\
    $v(\mathbf{r},t)$ & Mean membrane potential & mV \\
	$f(v\left(\mathbf{r},t\right))$ & Firing rate function & spikes.s$^{-1}$\\
	$e_t(\mathbf{r})$ & Field disturbance, with covariance function $\eta(\mathbf r-\mathbf r')$ & mV\\
	$\boldsymbol\epsilon_t$ & Observation noise, with covariance matrix $\Sigma_\epsilon$ & mV\\
	$m(\mathbf{r}_n)$ & Observation kernel where $n$ is sensor index $n=1,..,n_y$ & n.a. \\
	$w(\mathbf{r})$ & Spatial connectivity kernel & n.a.\\
	$h(t)$ & Post-synaptic response kernel & mV\\
	$\tau$, $\xi$ & Membrane time constant \& time constant parameter & s, n.a.\\
	$\delta(t)$ & Dirac-delta function & n.a.\\
	\hline    
	\multicolumn{3}{|c|}{\emph{Multi-resolution Approximation}} \\
	\hline                                                   
	$\phi_{j,l}(r)$&Scaling function&n.a\\
	$\psi_{j,l}(r)$&Wavelet function&n.a\\  
	$\alpha_{j_0,l}, \beta_{j,l}$&Connectivity kernel approximation and detail coefficients&mV~spike$^{-1}$\\ 
	$x_{t,j_{0},l},\check{x}_{t,j,l}$&Field approximation and detail coefficients at a given time&mV~spike$^{-1}$\\ 
	$N_m(r)$&$m$-th order B-spline function&n.a.\\
	$\varphi_m(r)$&$m$-th order B-spline wavelet function&n.a.\\
	\hline
	\multicolumn{3}{|c|}{\emph{Reduced Model}} \\
	\hline
		$\boldsymbol\mu(r)$&Vector of $n_x$ field scaling and wavelet functions&n.a.\\
		$\boldsymbol\lambda(r)$&Vector of $n_{\boldsymbol\theta}$ connectivity kernel scaling and wavelet functions&n.a.\\
   	$\mathbf{x}_t$ & State vector at time $t$ composed of  $x_{t,j_{0},l}$ and $\check{x}_{t,j,l}$ & mV\\ 
		$\boldsymbol\theta$&Vector of connectivity kernel parameters composed of $\alpha_{j_0,l}$ and $\beta_{j,l}$&mV\\ 
		$\boldsymbol{\Lambda}_x$&Inner product of field basis functions&n.a.\\
		$\boldsymbol\Gamma, \boldsymbol\Lambda_{\boldsymbol{\theta}}$&Decomposition connectivity matrices&n.a.\\
   	$\mathbf{w}_t$ & State disturbance vector, with covariance $\Sigma_w$ & mV\\ 
    $\mathbf{A}(\boldsymbol{\theta})$& State transition matrix& n.a.\\
   	$\mathbf{C}$ & Observation matrix & n.a. \\
	\hline
	\multicolumn{3}{|c|}{\emph{Frequency Analysis}} \\
	\hline
	$\boldsymbol{\nu}$, $\boldsymbol{\nu}_c$ & spatial frequency and spatial cutoff frequency & cycles/mm \\
	$\sigma_{\nu}^2$ & variance of Fourier transformed Gaussian basis function & (cycles/mm)$^2$\\
	\hline
	\multicolumn{3}{|c|}{\emph{Estimation}} \\
	\hline
	$\hat{\mathbf{x}}_t^{f-}$, $\hat{\mathbf{x}}_t^f$ & Forward prior and posterior state estimates & mV\\
	$\hat{\mathbf{x}}_t^{b}$ & Backward posterior state estimates & mV\\
	$P^{f-}_t$, $P^f_t$  & Forward prior and posterior covariance matrices & mV$^2$\\
	$P^b_t$ & Backward posterior covariance matrices & mV$^2$\\
	$M_t$& Cross-covariance matrix & mV$^2$\\
	$\mathcal K_{t} $ & Filter gain & n.a.\\ 
	$\mathcal S_{t} $ & Smoother gain & n.a.\\ 
	$\boldsymbol\Xi_1, \boldsymbol\Xi_0$&Expected covariance and cross-covariance matrices& mV$^2$\\ 
	$\mathcal{Q}(\boldsymbol{\theta},\boldsymbol\theta')$&Lower bound on log-likelihood function&n.a.\\
	$\boldsymbol\nu_0$, $\boldsymbol\nu_1$, $\boldsymbol\Upsilon$&Lower bound coefficient matrices&??\\
	\hline
\end{tabular}
\caption{\textbf{Notation.} The first column of the table gives the symbols for all the notation used in the paper. The second column provides a brief description of the quantity, and the third column provides the SI units where relevant.}
\label{tab:Notation}
\end{table*}  
\doublespacing

The single layer homogeneous neural field model in the most general form is described by the equation
\begin{equation}
	\label{FullDoubleIntModel} \underbrace{v\left(\mathbf{r},t\right)}_{\text{field}} =
	\int_{-\infty}^t 
	\underbrace{h\left(t - t'\right)}_{\text{synapse}} \int_\Omega
	\parham{\theta}\underbrace{w\left(\mathbf{r},\mathbf{r}'\right)}_{\text{connectivity}} 
	\underbrace{f\left( v\left( \mathbf{r}',t' \right)\right)}_{\text{firing}}
	\, \mathrm{d}\mathbf{r}'\mathrm{d}t',
\end{equation}
where the post-synaptic membrane voltage at time $t$ of a population of neurons at position $\mathbf r$ within the spatial domain $\Omega$ is denoted by $v\left(\mathbf r,t\right)$. The function $h(t)$ describes the post-synaptic response kernel, $w(\mathbf{r})$ describes the connectivity kernel \parham{in equation 2 its written $w(r,r')$} and $f(v(\mathbf{r},t))$ describes the relationship between the mean membrane potential and the mean firing rate. The parameter $\theta$ can be thought of the synaptic efficiency or coupling strength, where $\theta>0$ and $\theta<0$ describes excitation and inhibition, respectively. There are various forms of $h(t)$ that have been proposed in the literature, with different levels of complexity. These are shown in Fig.~\ref{fig:Modelcomponents}. Similarly, both the connectivity kernel and the activity function (firing rate) can take various forms. These are also shown in Fig.~\ref{fig:Modelcomponents}. The form of $w(\mathbf{r})$ typically describes an Laplacian (exponential) or Gaussian decay in connectivity strength from any point in the field. By assuming the form of $h(t)$ is the same across layers (scales) the Amari style neural field model is formed, incorporating a multilayer structure into the connectivity kernel. In this way, the connectivity kernel typically takes the form of a Mexican hat (Gaussian shape within layer connectivity) or Wizard hat (Laplacian shape within layer) as depicted in Fig.~\ref{fig:Modelcomponents}.

@@

The observation equation describing the intracranial electrophysiological recordings is given by
\begin{equation}\label{eq:ObservationEquation}
	y_t(\mathbf{r}_{n_y}) = \int_{\Omega} { m\left(\mathbf{r}_{n_y}-\mathbf{r}'\right) v_t\left(\mathbf{r}'\right) \, \mathrm{d}\mathbf{r}'} + \epsilon_t(\mathbf{r}_{n_y}), 
\end{equation}
where $m\left(\mathbf{r}_{n_y}-\mathbf{r}'\right)$ is the observation kernel at location $\mathbf{r}_{n_y}$ and  $\boldsymbol{\epsilon}_{t}\sim \mathcal{N}\left(\mathbf{0},\mathbf{\Sigma}_{\epsilon}\right)$  is an i.i.d. Gaussian white noise process with the covariance matrix $\mathbf{\Sigma}_{\epsilon}=\sigma^2_{\epsilon}\mathbf I_{n_y}$, where $\mathbf I$ denotes the identity matrix. \parham{The lead field parameters are not included in the observation equation as the intracranial recordings are considered here.}

@@

% At each spatial scale indexed by $j$ (level of decomposition), the neural field can be written as
% \begin{equation}
% 	v_{j,t}\left(\mathbf{r}\right) = \begin{cases}
% 	\sum_{l \in \mathbb{Z}}x_{j,l}(t) \underbrace{\phi_{j,l}\left(\mathbf{r}\right)}_{\text{scaling function}} + \check{x}_{t,j,l}\underbrace{\psi_{j,l}\left(\mathbf{r}\right)}_{\text{mother wavelet}} & \text{if $j=0$},\\
% 	\sum_{l \in \mathbb{Z}}\check{x}_{t,j,l}\psi_{j,l}\left(\mathbf{r}\right) & \text{otherwise}
% \end{cases}
% \end{equation}
The dynamic neural field is decomposed using
\begin{equation}
 v_t\left(r\right)=\sum_{l \in \mathbb{Z}}x_{t,j_{0},l} \underbrace{\phi_{j_0,l}\left(r\right)}_{\text{scaling functions}} + \sum_{j\geq j_0}^{\infty} \sum_{l \in \mathbb{Z}} \check{x}_{t,j,l} \underbrace{\psi_{j,l}\left(r\right)}_{\text{wavelets}},
\label{eq:FieldExpansion}
\end{equation}
where $x_{t,j_{0},l}$ and $\check{x}_{t,j,l} $ are the dynamic coefficients of the expansion, constituting the state vector at time $t$. The decomposition enables a separation of the static spatial characteristics, which are considered static functions, that are weighted by dynamic coefficients.

@@

\boldsymbol\theta^\top \triangleq& [\begin{array}{ccccc} \boldsymbol\alpha_{j_0}^\top & \boldsymbol\beta_{j_0}^\top & \boldsymbol\beta_{j_0+1}^\top & \cdots & \boldsymbol\beta_{j}^\top \end{array}] 

@@

\mathbf{x}_{t}^\top \triangleq& [\begin{array}{ccccc}\mathbf{x}_{t,j_{0}}^\top &  \check{\mathbf{x}}_{t,j_{0}}^\top & \check{\mathbf{x}}_{t,j_{0}+1}^\top & \cdots & \check{\mathbf{x}}_{t,j}^\top\end{array}]

@@

\boldsymbol\psi_{j}^\top(r)\end{array}\right] \\

@@

\boldsymbol\psi_{j}^\top(r)\end{array}\right],

@@

\parham{The state-transition equation can be simplified if the chosen family of scaling and wavelet functions are isotropic where}

@@

	\boldsymbol{\lambda}_{i}(r-r') = \boldsymbol{\lambda}(2\mathbf{c}_{i}+r'-r). 

@@

where $c_i$ is the centre of the $i$th basis function of the kernel decomposition. Following this, we can switch the order of operations with the inner product and convolution in Eq.~\eqref{eq:ApproxDiscreteTimeModel4}. With this switch the convolution is now between the scaling functions and wavelets for the field and the scaling functions and wavelets for the connectivity kernel. This convolution can be calculated analytically when using B-spline scaling and wavelet functions and can be predefined once, since these are static functions. This has major computation advantages when solving the estimation problem. \parham{Although this switch holds theoretically it should be noted that it will introduce numerical error, specially close to the edges, due to the finite extent of the field. } The predefined convolution can be written as

@@

	\left[\Gamma(r')\right]_{:i} = T_s \mathbf{\Lambda}_{x}^{-1}\int_{\Omega} \boldsymbol\mu\left(r\right)\boldsymbol\lambda\left(2c_{i} + r'-r\right) \,\mathrm{d}r,

@@

 where $\left[\Gamma(r')\right]_{:i}$ denotes the $i$th column of  $\left[\Gamma(r')\right]$ giving

@@

	\mathbf{y}_t = \mathbf{C}\mathbf{x}_t + \boldsymbol{\epsilon}_t,

@@

In this paper, we have presented a novel model-based framework for estimating cortical dynamics from electrophysiological measurements. The novel and key developments of the paper include the multi-resolution FEM representation of the neural field, and the estimator for an intracortical connectivity kernel with an arbitrary shape. This work is significant, as the ability to create patient specific neural field models has the potential to contribute to our understanding and improve treatment of diseases resulting from abnormal neurodynamics, such as epilepsy. Other groups have previously highlighted the importance of a multi-resolution approach in neural field modeling. It is thought that the dynamics and connectivity structure differs at different spatial scales~\citep{Qubbaj2009,Breakspear2005,Schultze-Kraft2010}. %\dean{This is a test to see if we can fit something about Breaky's paper in here. It would be nice to slot something in here because he used wavelets.}

@@

Another extension of this framework is the inclusion of finite distant-dependent action potential propagation velocity into the parametric neural field equations. In small networks the delays via propagation can be neglected, however they must be accounted for in large scale networks. For instance, it is shown by \citet{Ghosh2008} that inclusion of time delays arising from propagation along connecting \parham{fibres} are essential for the fluctuations to be appeared in the default networks. Finally, future work should be directed towards applying and validating the framework on real data.
\newpage
\appendix
\section{Inner product of two B-spline scaling functions}\label{ap:InnerProductOfBsplines}
In this section, an analytic formula is derived for the inner product of two B-spline scaling functions. Consider two B-spline scaling functions of order $m$ and $m'$. The support of $N_m\left(s\right)$ is $\left[ 0,m\right]$ and  is symmetric with respect to $r=\frac{m}{2}$, i.e.
\begin{align}\label{eq:APP-SymmetrySplieEq}
 N_{m}\left(\frac{m}{2}+r\right)=N_{m}\left(\frac{m}{2}-r\right).
\end{align}
A direct consequence of Eq.~\eqref{eq:APP-SymmetrySplieEq} is 
\begin{align}
 N_{m}\left(r\right)=N_{m}\left(m-r\right).
\end{align}
Therefore
\begin{align}
\int_{-\infty}^{+\infty}N_{m}\left(r-l_{1}\right)N_{m'}\left(r-l_{2}\right)dr&=\int_{-\infty}^{+\infty}N_{m}\left(m-r+l_{1}\right)N_{m'}\left(r-l_{2}\right)dr \nonumber \\
&=\int_{-\infty}^{+\infty}N_{m}\left(m+l_{1}-l_{2}-u\right)N_{m'}\left(u\right)du \nonumber \\
&=\left(N_m \ast N_{m'}\right) \left(m+l_{1}-l_{2}\right) \nonumber \\
&=N_{m+m'}\left(m+l_{1}-l_{2}\right) \nonumber \\
&=N_{m+m'}\left(m'+l_{2}-l_{1}\right).
\end{align}
\section{Scaling function expansion}\label{ap:Induction}  
In this appendix we show by induction that how the scaling function at $j=0$ can be written in terms of the scaling function at level $j$. For $n_1$ in  Eq.~\eqref{eq:MRA-ConvertingFormulaForscalingFunctions} we have
\begin{align}
 N_{m}\left(r\right)&=\sum_{n_1=0}^{m} \left[\mathbf p\right]_{n_1} N_{m}\left(2r-n_1\right) \label{eq:App-TwoScalepair1},
  \end{align}
which clearly holds from two-scale relation pair (see Eq.~\eqref{eq:MRA-TwoScalepair1}). Now assuming Eq.~\eqref{eq:MRA-ConvertingFormulaForscalingFunctions} for $n_{j-1}$ we can write 
\begin{align}\label{eq:app-ConvertingFormulaForscalingFunctions}
 &N_m(r)=\nonumber \\
&\sum_{n_1,n_2, \dots n_{j-1}=0}^{m}\left[\mathbf p\right]_{n_1} \left[\mathbf p\right]_{n_2}\dots \left[\mathbf p\right]_{n_{j-1}}N_m(2^{j-1}r-k_{n_1,n_2, \dots, n_{j-1}}),
\end{align}
in which $N_m(2^{j-1}r-k_{n_1,n_2, \dots, n_{j-1}})$ can be written in terms of $N_m(2^{j}r)$ as
\begin{align}\label{eq:AppendixNj-1intermsofNj}
 &N_m(2^{j-1}r-k_{n_1,n_2, \dots, n_{j-1}})=\nonumber \\
&\sum_{n_j=0}^m \left[\mathbf p\right]_{n_j}N_m(2^jr-2\times k_{n_1,n_2, \dots, n_{j-1}}-n_j)\nonumber \\
&=\sum_{n_j=0}^m \left[\mathbf p\right]_{n_j}N_m(2^jr- k_{n_1,n_2, \dots, n_{j}}).
\end{align}
Substituting Eq.~\eqref{eq:AppendixNj-1intermsofNj} into Eq.~\eqref{eq:MRA-ConvertingFormulaForscalingFunctions} completes the proof.
